---
title: "Red wine white wine pred"
author: "Maiga"
date: "12/11/2019"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---
#Packages
```{r}
library(tidyverse)
library(caret)
library(ggplot2)
library(e1071)
library(rpart)
library(randomForest)
```

#data
```{r}
redwine <- readr::read_delim("https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality-red.csv", delim = ";")

whitewine <- readr::read_delim("https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality-white.csv", delim = ";")

#Used to fixe names
names(redwine) <- janitor::make_clean_names(names(redwine))
names(whitewine) <- janitor::make_clean_names(names(whitewine))
View(redwine)
View(whitewine)

```
Same number of columns and names of columns for both dataset

#Need to put quality as factor to avoid complications later
```{r}
head(redwine)
redwine$quality = as.factor(redwine$quality)
head(redwine)
whitewine$quality = as.factor(whitewine$quality)
head(whitewine)
```

#Data visualization and inspection
  #Missing values
```{r}
length(which(!complete.cases(redwine)))
length(which(!complete.cases(whitewine)))
```
  #Visualization redwine
  
```{r}
redwine %>% gather(var, value, -quality) %>%
  ggplot(aes(quality, value, fill = quality)) +
  geom_boxplot() +
  facet_wrap('var', scales = "free", ncol = 3)
  

```

#Visualization whitewine
```{r}
whitewine %>% gather(var, value, -quality) %>%
  ggplot(aes(quality, value, fill = quality)) +
  geom_boxplot() +
  facet_wrap('var', scales = "free", ncol = 3)
  


```
# Data partition
```{r}
set.seed(2) # makes the random selection of rows reproducible
train1 <- redwine$quality %>%
          createDataPartition(p = 0.70, list = FALSE)
#head(train)

redTrain <- redwine[train1,]
redTest <- redwine[-train1,]


head(redTest)
```


#rpart on red wine, training
```{r}
fitRed <- rpart(quality ~ ., data = redTrain)
fitRed
plot(fitRed)
text(fitRed,cex = 0.8)
```
#Testing on redwine
```{r}
predRed <- predict(fitRed, newdata = redTest)
#confusionMatrix(data = predRed,reference =redTest$quality)
typeof(predRed)
```
Probleme avec la matrice de confusion pas les memes types de donnees.

#random forest on red wine, training
```{r}
fitrr <- randomForest(quality ~ ., data = redTrain)
fitrr
plot(fitrr)
```
#Testing on redwine
```{r}
predRedr <- predict(fitrr, newdata = redTest)
confusionMatrix(data = predRedr,reference =redTest$quality)
typeof(predRedr)
```

#Rpart on white wine
  #Data partition
```{r}
set.seed(3) # makes the random selection of rows reproducible
train2 <- whitewine$quality %>%
          createDataPartition(p = 0.70, list = FALSE)
#head(train)

wTrain <- whitewine[train2,]
wTest <- whitewine[-train2,]


head(wTest)
```

```{r}
fitWhite <- rpart(quality ~ ., data = wTrain)
fitWhite
plot(fitWhite)
text(fitWhite,cex = 0.8)
```
#Testing on white wine
```{r}
predwhite <- predict(fitWhite, newdata = wTest)
#confusionMatrix(data = predRed,reference =redTest$quality)
typeof(predwhite)
```

#New columns in red and white
```{r}
#red wine
redwine$type = 'red' #create a new columns
redwine$type = as.factor(redwine$type) #convert it into factor
glimpse(redwine)
#white wine
whitewine$type = 'white' #create a new columns
whitewine$type = as.factor(whitewine$type) #convert it into factor
glimpse(whitewine)

```

#Joinning red and white
```{r}
redwhite = full_join(redwine, whitewine)
glimpse(redwhite)

```

#As factor again don't know why it didn't conserve the modification
```{r}
redwhite$type = as.factor(redwhite$type) #convert it into factor
redwhite$quality = as.factor(redwhite$quality) #convert it into factor
glimpse(redwhite)
```

#Random forest on join data to predict wine type.

# 1-Data partition
```{r}
set.seed(6) # makes the random selection of rows reproducible
train <- redwhite$type %>%
          createDataPartition(p = 0.70, list = FALSE)
#head(train)

rwTrain <- redwhite[train,]
rwTest <- redwhite[-train,]


head(rwTrain)
```

#Train
```{r}
fit3 <- randomForest(type~., data = rwTrain) 
plot(fit3)
```
# Test data and confusion matrix
```{r}
pred <- predict(fit3, newdata = rwTest)
confusionMatrix(data = pred,reference =rwTest$type)
#View(pred)
```

#Quality of wine from joined data

```{r}
fit4 <- randomForest(quality~., data = rwTrain) 
plot(fit4)
```

#Testing
```{r}
pred2 <- predict(fit4, newdata = rwTest)
confusionMatrix(data = pred2,reference =rwTest$quality)
```

